The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-14 src/ms.tex
remove subsubsections for learn
working affiliated package table, but missing citations
pass through dev key / token

assert and remove except

undo dev key overengineering - it should be fine with the env var

upload ms pdf file artifact

ok now i remember - PRs done have access to repository secrets
Add section for Data Central/AAT Archive

As defined in \paperii, Astropy affiliated packages are astronomy-related
\python packages that provide functionality that builds upon and extends the
\astropypkg core package that have requested to be included as part of the
Astropy Project community. These packages support the goals and vision of
Astropy of improving code re-use, interoperability, and embracing good coding
practices such as testing and thorough documentation.
All Astropy-coordinated and other affiliated packages are listed on the astropy
website.\footnote{\url{https://www.astropy.org/affiliated}}

@@

\todo{APW}{Add a table of all affiliated packages, like in the previous paper}

@@

@@

\subsubsection{Current status and scope}

@@

\subsubsection{Learn vision for the future}

@@

\bibliographystyle{aasjournal}
\bibliography{refs}

% \appendix

% \section{List of Affiliated Packages}

% \begin{longrotatetable}
%     \begin{deluxetable*}{cccp{3in}c}
%     \tablecaption{Registry of affiliated packages.}
%     \label{tab:registry}
%     \tablehead{
%         \colhead{Package Name} &
%         \colhead{Stable} &
%         \colhead{PyPI Name} &
%         \colhead{Maintainer} &
%         \colhead{Citation}
%       }
%       \startdata
%         \input{registry.tex}
%       \enddata
%   \end{deluxetable*}
% \end{longrotatetable}

>>>>

As defined in \paperii, Astropy affiliated packages are astronomy-related
\python packages that provide functionality that builds upon and extends the
\astropypkg core package that have requested to be included as part of the
Astropy Project community. These packages support the goals and vision of
Astropy of improving code re-use, interoperability, and embracing good coding
practices such as testing and thorough documentation.
All Astropy-coordinated and other affiliated packages are listed with detailed
information on the \href{{https://www.astropy.org/affiliated}}{\astropy
website}; A table summarizing key aspects of the affiliated packages is included
in the Appendix below (Table~\ref{tab:affiliated-registry}).

@@

@@

\subsubsection{Data Central and the Anglo-Australian Telescope Archive}
\secauthor{James Tocknell}
Data Central is one of the five Australian Virtual Observatory\footnote{known as
  the All-Sky Virtual Observatory, or ASVO} nodes, providing both Australian and
international astronomers access to and services for surveys of the southern
sky. Whilst primarily hosting optical data, including the Anglo-Australian
Telescope (AAT) Archive\footnote{The AAT Archive is currently jointly managed by
  Data Central, Astronomy Australia Limited (AAL), and National Computational
  Infrastructure (NCI)}, Data Central also assists theoretical and radio
astronomers host and manage their data.

Python is widely used by Data Central, and \astropy and its wider ecosystem play
a vital role in the initial ingestion, reduction, access and visualisation of
the hosted data and services. For example, the AAT Archive hosts data back to
1974, so \astropycoordinates, \astropytime and \astropyfits are used to ingest
data flowing from the AAT to ensure that a consistent time and coordinate
system is provided to users for simpler querying.

As many of the surveys hosted by Data Central are spectroscopic surveys from the
AAT, specutils is heavily used to standardise the variety of encodings of
spectroscopic data into a form easily readable and visualisable by many standard
tools (such as ds9 or splat). Data Central has upstreamed into specutils loaders
for all hosted spectra, including 2dfdr-reduced spectra from the AAT Archive,
and strongly encourages other archives to provide loaders for their data to
further reuse of existing archival data.

@@

% \subsubsection{Current status and scope}

@@

% \subsubsection{Learn vision for the future}

@@

\bibliographystyle{aasjournal}
\bibliography{refs, static/affiliated-refs}

\appendix

\section{List of Affiliated Packages}

\begin{longrotatetable}
    \begin{deluxetable*}{ccp{2in}p{2.5in}}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:affiliated-registry}
    \tablehead{
        \colhead{Package Name} &
        % \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer(s)} &
        \colhead{Citation(s)}
      }
      \startdata
        \input{generated/affiliated-table.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}
